---
title: "R_econometric_analysis"
output: html_document
date: "2025-07-29"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(fixest)
# library(stargazer)
library(modelsummary)
library(stringr)
library(ggplot2)
source("R_scripts/helper_functions.R")
```

# Import buffer dfs
- for the larger buffer radius, filtering values == True - this serves as the filter to identify all the control group properties
- for the inner buffer radius, values that are True serve as the treatment group that are within the smaller radius, if they are True within the smaller radius, they must be True for the larger radius
- for the post treatment (POST* columns), filter the ones that correspond to the larger buffer radius
```{r}
# import file that is already trimmed by date and by the largest control group i.e. 1000m buffer radius
buffer_df <- read.csv(file.path(getwd(),"Exported_Data","flood_buffer_dist","processed_df",
                      "master_treat_post_buffer_trimmed12months_localDID.csv"))

buffer_df
```

# E1.0 - Event study (flood causality)

```{r}
# params
y_var <- "log_price_PSM"
property_type <- "Condominium/Apartment"
# cluster_vars <- c("SUBZONE_N")
# fe_vars <- c("Project_Name","month_year")
# cluster_vars <- c("SUBZONE_N")
# fe_vars <- c("SUBZONE_N","month_year")
cluster_vars <- c("PLN_AREA_N")
fe_vars <- c("SUBZONE_N","month_year")

# event study period
months_post_flood <- c(1:12)


local_DID_df_list = list()
i = 1 # counter
for (small_radius in seq(50, 450, by = 50)) { # length=9
  for (big_radius in seq(500, 1000, by = 50)){ # length=11
    # params
    # treatment vars
    treatment_vars <- sprintf("TREAT_d%s",small_radius)
    # post treatment vars
    post_treatment_vars <- sprintf("POST_%s_months_d%s", months_post_flood, big_radius)
    # control variables
    control_vars <- c("Type_of_Sale","Area_.SQM.","Building_Age","Floor_level","is_ground_floor")

    # get local DID df
    local_DID_df <- get_local_DID_df(buffer_df, small_radius=small_radius, big_radius=big_radius,
                                     months_post_flood=months_post_flood,
                     y_var=y_var, fe_vars=fe_vars, cluster_vars=cluster_vars) 
    
    # fit event study model
    model_property_formula <- feols_formula(y_var = y_var,
                                            control_vars=control_vars,
                                            interaction_vars = interaction_combinations(
                                                  treatment = treatment_vars,
                                                  post_treatment = post_treatment_vars
                                                ),
                                            interaction_sep = "*",
                                            fe_vars = fe_vars,
                                            cluster_vars = cluster_vars)
      
    # model_property_formula
    
    # model where fixed effects are project name and month_year
    model_property <- feols(
      model_property_formula$formula,
      cluster = model_property_formula$cluster,
      data = local_DID_df%>%
        filter(Property_Type == property_type)
    )
    
    # print(summary(model_property))
    model_property_df <- etable(model_property)
    # to remove all associated classes and getting the fundamental data structures to create my own df, becus etable doesnt allow exporting into csv
    model_property_df <- unclass(etable(model_property))
    # print(model_property_df)
    df <- data.frame(Vars = model_property_df[[1]], model_results = model_property_df$model_property,
                     extract_model_results(model_property_df$model_property))
    # add additional rows for edj R2
    df[nrow(df)+1,] <- c("Adjusted R2",fitstat(model_property, "ar2")[[1]], rep(NA, times=ncol(df)-2))
    # add column to identify which robustness test we are looking at - good for long format
    df$Robustness_test <- sprintf("Treat%s_Control%s",small_radius, big_radius)
    
    local_DID_df_list[[i]] <- df
    # increase counter
    i = i+1
    df
  }
}

local_DID_df_list <- as.data.frame(do.call(rbind, local_DID_df_list))
local_DID_df_list
# write.csv(local_DID_df_list,file.path(getwd(),"Exported_Data","flood_buffer_dist","processed_df",
#                       sprintf("model_trimmed12months_localDID_%s_CLUSTER%s_FE%s.csv",y_var,cluster_vars[1],fe_vars[1])),
#           row.names = FALSE)
```



## Get statistics of robustness test

```{r}
# params
y_var <- "log_price_PSM"
# cluster_vars <- c("SUBZONE_N")
# fe_vars <- c("Project_Name","month_year")
# cluster_vars <- c("SUBZONE_N")
# fe_vars <- c("SUBZONE_N","month_year")
cluster_vars <- c("PLN_AREA_N")
fe_vars <- c("SUBZONE_N","month_year")

filename <- sprintf("model_trimmed12months_localDID_%s_CLUSTER%s_FE%s",y_var,cluster_vars[1],fe_vars[1])
read.csv(file.path(getwd(),"Exported_Data","flood_buffer_dist","processed_df",
                                         sprintf("%s.csv",filename)))%>%
  # filter(Vars=="Adjusted R2")%>%
  # summarise(min_adj_r2 = min(model_results), max_adj_r2 = max(model_results))
  filter(Vars=="Observations")%>%
  mutate_at(vars(model_results), function(x) as.numeric(sub(",","",x)))%>%
  summarise(min_obs = min(model_results), max_obs = max(model_results))
```
## Plot radius buffer robustness test

```{r}
# params
y_var <- "log_price_PSM"

lapply(list(
  list(cluster_vars = c("SUBZONE_N"), fe_vars = c("Project_Name","month_year")),
  list(cluster_vars = c("SUBZONE_N"), fe_vars = c("SUBZONE_N","month_year")),
  list(cluster_vars = c("PLN_AREA_N"), fe_vars = c("SUBZONE_N","month_year"))
  ), function(x){
    filename <- sprintf("model_trimmed12months_localDID_%s_CLUSTER%s_FE%s",y_var,
                        x$cluster_vars[1],x$fe_vars[1])
    # plot and save heat map
    plot_local_DID_robustness(fp = file.path(getwd(),"Exported_Data","flood_buffer_dist","processed_df",
                                             sprintf("%s.csv",filename)),
                          save_fp = file.path(getwd(),"Exported_Data","exported_figures",sprintf("%s.svg",filename)))
    filename
  })

```



# Varying buffer distance
## B1.0 Baseline


```{r}
# params
y_var <- "log_price_PSM"
property_type <- "Condominium/Apartment"
cluster_vars <- c("SUBZONE_N")
fe_vars <- c("Project_Name","month_year")
# read file
fp <- buffer_time_period_fps[1]

for (fp in buffer_time_period_fps){
  buffer_time_period <- read.csv(fp)
  buffer_param <- str_extract(basename(fp), "(?<=buffer)(.*?)(?=_network.*?)")
  
  # select columns
  transaction_df <- buffer_time_period%>%
                        # y-dependent variable
                        mutate(log_price_PSM = log(Unit_Price_.._PSM.),
                               log_price = log(Transacted_Price_...),
                               month_year = paste(month, year, sep = "_")
                               )%>%
                        select(c(y_var, Type_of_Sale,
                                 Area_.SQM.,Building_Age,Floor_level,is_ground_floor,
                                 sprintf("within_%s_months_post_flood",months_post_flood),
                                 month_year,
                                 "Project_Name","SUBZONE_N","Property_Type"
                                 ))%>%
    # convert to boolean
      mutate_at(c(sprintf("within_%s_months_post_flood",months_post_flood),
                  "is_ground_floor"),as.logical)%>%
      mutate(across(where(is.character), as.factor))
  
  # how many flooded properties
  print(sprintf("Number of flooded properties: %s",sum(transaction_df$within_2_months_post_flood)))
  # transaction_df
  
  model_property_formula <- feols_formula(y_var = y_var,
                                        control_vars=names(transaction_df),
                                        interaction_vars = NA,
                                        interaction_sep = "*",
                                        fe_vars = fe_vars,
                                        cluster_vars = cluster_vars)
  
  # model_property_formula
  
  # model where fixed effects are project name and month_year
  model_property <- feols(
    model_property_formula$formula,
    cluster = model_property_formula$cluster,
    data = transaction_df%>%
      filter(Property_Type == property_type)
  )
  adjr2 <- fitstat(model_property, "ar2")[[1]]
  # model_property
  # print(summary(model_property))
  print(sprintf("Buffer = %s m - Adj R2: %.3f",buffer_param,adjr2))
}

# model_property_df <- etable(model_property)
# model_property_df$FE <- fe
# model_property_df$Property_Type <- property_type
# model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]

```

# Import transaction_df

```{r}
flood_residential_fp <- file.path(getwd(),"Exported_Data",
                                  "floodPrivateResidential_20260210_buffer200_networkDepth2_adaptationProjectName.csv")

fe_vars <- c("Project_Name","month_year") #c("Building_Name","month_year") # or c("Project_Name","month_year")
cluster_vars <- c(fe_vars[1])
y_var <-"log_price_PSM"  #or "log_price"
# test flood exposure one at a time, not all together because then there would be multicollinearity
hazard_var <- "within_6_months_post_flood"
months_post_flood <- c(1,2,3)

transaction_df <- get_transaction_df(fp=flood_residential_fp, 
                                     y_var=y_var,
                                     fe_vars=fe_vars,
                                     months_post_flood=months_post_flood)

transaction_df
```

```{r}
names(transaction_df)
```

## unique filename for saving results
```{r}
# unique filename
save_fp <- unlist(strsplit(basename(flood_residential_fp),"[_.]"))
save_fp <- save_fp[length(save_fp)-1]
save_fp <-paste(c(save_fp,paste(fe_vars,collapse="-"),y_var),collapse="_")
save_fp
```


## vars_absorbed_by_FE

```{r}
vars_absorbed_by_FE <- c("Tenure",                                       # absorbed by strong project/building FEs
            "DOWNTOWN_CORE_travel_time","TAMPINES_travel_time",      # absorbed by strong project/building FEs
            "WOODLANDS_travel_time","ANG_MO_KIO_travel_time",        # absorbed by strong project/building FEs
            "JURONG_EAST_travel_time", # absorbed by strong project/building FEs
            "min_travel_time_work","sch_within_1km_car",             # absorbed by strong project/building FEs
            "sch_within_2km_car","sch_min_distance_car",             # absorbed by strong project/building FEs
            "sch_within_1km_walk","sch_within_2km_walk",             # absorbed by strong project/building FEs
            "betweeness_centrality","closeness_centrality",          # absorbed by strong project/building FEs
            "sch_min_distance_walk","malls_within_400m",             # absorbed by strong project/building FEs
            "parks_within_400m")
```


# Hedonic models (baseline)

```{r}
fps <- c("floodPrivateResidential_20260210_buffer200_networkDepth2_adaptationProjectName.csv", 
         "floodPrivateResidential_20260210_buffer200_networkDepthNone_adaptationProjectName.csv")

fps <- file.path(getwd(),"Exported_Data", fps)
fps

```
```{r}
names(transaction_df)
```
# 1.0 Multiple time period Event studies

## 1.1 Baseline

```{r}
model_property_df_list = list()
i = 1
for (fp in fps) {
  for (fe in c("Project_Name","Building_Name")){
  # for (fe in c("SUBZONE_N","PLN_AREA_N")){
    for (property_type in c("Condominium/Apartment","Landed")){
    # for (property_type in c("Condominium/Apartment")){
      print(fp)
      # feols inputs
      fe_vars <- c(fe, "month_year")
      cluster_vars <- c(fe_vars[1])
      
      # transaction df
      transaction_df <- get_transaction_df(fp, y_var = y_var, 
                         fe_vars = fe_vars, months_post_flood = months_post_flood)
      
      # remove building FE
      transaction_df <- transaction_df%>%
        select(-vars_absorbed_by_FE)
      
      model_property_formula <- feols_formula(y_var = y_var,
                                              control_vars=setdiff(
                                                names(transaction_df),
                                                     c("within_flooding_hotspot","prone_to_high_tide",
                                                       "work_categories","drainage_period","near_mrt"
                                                       # "time_since_flood"
                                                       )),
                    interaction_vars = NA,
                    # interaction_vars = NA,
                    interaction_sep = "*",
                    fe_vars = fe_vars,
                    cluster_vars = cluster_vars)
      
      model_property_formula
      
      # model where fixed effects are project name and month_year
      model_property <- feols(
        model_property_formula$formula,
        cluster = model_property_formula$cluster,
        data = transaction_df%>%
          filter(Property_Type == property_type)
      )
      print(summary(model_property))
      # # display model outputs
      # print(etable(model_property))
      model_property_df <- etable(model_property)
      model_property_df$FE <- fe
      model_property_df$Property_Type <- property_type
      model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]
      model_property_df$filepath <- basename(fp)
      # print(model_property_df)
      model_property_df_list[[i]] <- model_property_df
      # increase counter
      i = i+1
    }
  }
}

model_property_df <- as.data.frame(do.call(rbind, model_property_df_list))
model_property_df

# write.csv(model_property_df, file = file.path(getwd(),"Exported_Data","model_summaries_df",
#                                               sprintf("%s_%s.csv", y_var,Sys.Date())))
```

## 1.2 GF interaction

```{r}
model_property_df_list = list()
i = 1
for (fp in fps) {
  for (fe in c("Project_Name","Building_Name")){
  # for (fe in c("SUBZONE_N","PLN_AREA_N")){
    # for (property_type in c("Condominium/Apartment","Landed")){
    for (property_type in c("Condominium/Apartment")){
      print(fp)
      # feols inputs
      fe_vars <- c(fe, "month_year")
      cluster_vars <- c(fe_vars[1])
      
      # transaction df
      transaction_df <- get_transaction_df(fp, y_var = y_var, 
                         fe_vars = fe_vars, months_post_flood = months_post_flood)
      
      # remove building FE
      transaction_df <- transaction_df%>%
        select(-vars_absorbed_by_FE)
      
      model_property_formula <- feols_formula(y_var = y_var,
                                              control_vars=setdiff(
                                                names(transaction_df),
                                                     c("within_flooding_hotspot","prone_to_high_tide",
                                                       "work_categories","drainage_period","near_mrt",
                                                       "time_since_flood")),
                    interaction_vars = interaction_combinations(
                                      hazards = sprintf("within_%s_months_post_flood",months_post_flood),
                                      vulnerability = c("is_ground_floor")
                                    ),
                    # interaction_vars = NA,
                    interaction_sep = "*",
                    fe_vars = fe_vars,
                    cluster_vars = cluster_vars)
      
      model_property_formula
      
      # model where fixed effects are project name and month_year
      model_property <- feols(
        model_property_formula$formula,
        cluster = model_property_formula$cluster,
        data = transaction_df%>%
          filter(Property_Type == property_type)
      )
      print(summary(model_property))
      # # display model outputs
      # print(etable(model_property))
      model_property_df <- etable(model_property)
      model_property_df$FE <- fe
      model_property_df$Property_Type <- property_type
      model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]
      model_property_df$filepath <- basename(fp)
      # print(model_property_df)
      model_property_df_list[[i]] <- model_property_df
      # increase counter
      i = i+1
    }
  }
}

model_property_df <- as.data.frame(do.call(rbind, model_property_df_list))
model_property_df

# write.csv(model_property_df, file = file.path(getwd(),"Exported_Data","model_summaries_df",
#                                               sprintf("%s_GF_%s.csv", y_var,Sys.Date())))
```

## 1.3 (A) Tide prone interactions (non-landed)


```{r}
model_property_df_list = list()
i = 1
for (fp in fps) {
  for (fe in c("Project_Name","Building_Name")){
  # for (fe in c("SUBZONE_N","PLN_AREA_N")){
    # for (property_type in c("Condominium/Apartment","Landed")){
    for (property_type in c("Condominium/Apartment")){
      print(fp)
      # feols inputs
      fe_vars <- c(fe, "month_year")
      cluster_vars <- c(fe_vars[1])
      
      # transaction df
      transaction_df <- get_transaction_df(fp, y_var = y_var, 
                         fe_vars = fe_vars, months_post_flood = months_post_flood)
      
      # remove building FE
      transaction_df <- transaction_df%>%
        select(-vars_absorbed_by_FE)
      
      model_property_formula <- feols_formula(y_var = y_var,
                                              control_vars=setdiff(
                                                names(transaction_df),
                                                     c("within_flooding_hotspot",
                                                       "work_categories","drainage_period","near_mrt",
                                                       "time_since_flood")),
                    interaction_vars = interaction_combinations(
                                      hazards = c(sprintf("within_%s_months_post_flood",months_post_flood),
                                                  "Floor_level","is_ground_floor"),
                                      vulnerability = c("prone_to_high_tide")
                                    ),
                    # specified_interaction_vars = c("prone_to_high_tide * Floor_level",
                    #                                "prone_to_high_tide * is_ground_floor",
                    #                                # sprintf("prone_to_high_tide * within_%s_months_post_flood",months_post_flood[2])
                    #                                ),
                    # interaction_vars = NA,
                    interaction_sep = "*",
                    fe_vars = fe_vars,
                    cluster_vars = cluster_vars)
      
      print(model_property_formula)
      
      # model where fixed effects are project name and month_year
      model_property <- feols(
        model_property_formula$formula,
        cluster = model_property_formula$cluster,
        data = transaction_df%>%
          filter(Property_Type == property_type)
      )
      print(summary(model_property))
      # # display model outputs
      # print(etable(model_property))
      model_property_df <- etable(model_property)
      model_property_df$FE <- fe
      model_property_df$Property_Type <- property_type
      model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]
      model_property_df$filepath <- basename(fp)
      # print(model_property_df)
      model_property_df_list[[i]] <- model_property_df
      # increase counter
      i = i+1
    }
  }
}

model_property_df <- as.data.frame(do.call(rbind, model_property_df_list))
model_property_df

# write.csv(model_property_df, file = file.path(getwd(),"Exported_Data","model_summaries_df",
#                                               sprintf("%s_Tideprone_nonlanded_%s.csv", y_var,Sys.Date())))
```

## 1.3 (B) Tide prone interactions - landed


```{r}
model_property_df_list = list()
i = 1
for (fp in fps) {
  for (fe in c("Project_Name","Building_Name")){
  # for (fe in c("SUBZONE_N","PLN_AREA_N")){
    # for (property_type in c("Condominium/Apartment","Landed")){
    for (property_type in c("Landed")){
      print(fp)
      # feols inputs
      fe_vars <- c(fe, "month_year")
      cluster_vars <- c(fe_vars[1])
      
      # transaction df
      transaction_df <- get_transaction_df(fp, y_var = y_var, 
                         fe_vars = fe_vars, months_post_flood = months_post_flood)
      
      # remove building FE
      transaction_df <- transaction_df%>%
        select(-vars_absorbed_by_FE)
      
      model_property_formula <- feols_formula(y_var = y_var,
                                              control_vars=setdiff(
                                                names(transaction_df),
                                                     c(sprintf("within_%s_months_post_flood",months_post_flood),
                                                       "work_categories","drainage_period","near_mrt",
                                                       "time_since_flood")),
                    interaction_vars = interaction_combinations(
                                      # hazards = sprintf("within_%s_months_post_flood",months_post_flood),
                                      hazards = c("within_flooding_hotspot"),
                                      vulnerability = c("prone_to_high_tide")
                                    ),
                    # specified_interaction_vars = c("prone_to_high_tide * Floor_level",
                    #                                "prone_to_high_tide * is_ground_floor",
                    #                                # sprintf("prone_to_high_tide * within_%s_months_post_flood",months_post_flood[2])
                    #                                ),
                    # interaction_vars = NA,
                    interaction_sep = "*",
                    fe_vars = fe_vars,
                    cluster_vars = cluster_vars)
      
      print(model_property_formula)
      
      # model where fixed effects are project name and month_year
      model_property <- feols(
        model_property_formula$formula,
        cluster = model_property_formula$cluster,
        data = transaction_df%>%
          filter(Property_Type == property_type)
      )
      print(summary(model_property))
      # # display model outputs
      # print(etable(model_property))
      model_property_df <- etable(model_property)
      model_property_df$FE <- fe
      model_property_df$Property_Type <- property_type
      model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]
      model_property_df$filepath <- basename(fp)
      # print(model_property_df)
      model_property_df_list[[i]] <- model_property_df
      # increase counter
      i = i+1
    }
  }
}

model_property_df <- as.data.frame(do.call(rbind, model_property_df_list))
model_property_df

# write.csv(model_property_df, file = file.path(getwd(),"Exported_Data","model_summaries_df",
#                                               sprintf("%s_Tideprone_landed_%s.csv", y_var,Sys.Date())))
```

## 1.4 Adaptation interactions


```{r}
model_property_df_list = list()
i = 1
for (fp in fps) {
  for (fe in c("Project_Name","Building_Name")){
  # for (fe in c("SUBZONE_N","PLN_AREA_N")){
    for (property_type in c("Condominium/Apartment","Landed")){
    # for (property_type in c("Condominium/Apartment")){
      print(fp)
      # feols inputs
      fe_vars <- c(fe, "month_year")
      cluster_vars <- c(fe_vars[1])
      
      # transaction df
      transaction_df <- get_transaction_df(fp, y_var = y_var, 
                         fe_vars = fe_vars, months_post_flood = months_post_flood)
      
      # remove building FE
      transaction_df <- transaction_df%>%
        select(-vars_absorbed_by_FE)
      
      model_property_formula <- feols_formula(y_var = y_var,
                                              control_vars=setdiff(
                                                names(transaction_df),
                                                     c("prone_to_high_tide",
                                                       "work_categories","drainage_period","near_mrt",
                                                       "time_since_flood",
                                                       sprintf("within_%s_months_post_flood",months_post_flood)
                                                       )),
                    # interaction_vars = interaction_combinations(
                    #                   hazards = c(sprintf("within_%s_months_post_flood",months_post_flood),
                    #                               "Floor_level","is_ground_floor"),
                    #                   response = c("prone_to_high_tide")
                    #                 ),
                    specified_interaction_vars = c("work_categories : drainage_period",
                                                   "work_categories : drainage_period : within_flooding_hotspot",
                                                   sprintf("work_categories : drainage_period : within_%s_months_post_flood",months_post_flood[2])
                                                   ),
                    # interaction_vars = NA,
                    interaction_sep = "*",
                    fe_vars = fe_vars,
                    cluster_vars = cluster_vars)
      
      print(model_property_formula)
      
      # model where fixed effects are project name and month_year
      model_property <- feols(
        model_property_formula$formula,
        cluster = model_property_formula$cluster,
        data = transaction_df%>%
          filter(Property_Type == property_type)
      )
      print(summary(model_property))
      # # display model outputs
      # print(etable(model_property))
      model_property_df <- etable(model_property)
      model_property_df$FE <- fe
      model_property_df$Property_Type <- property_type
      model_property_df$AdjR2 <- fitstat(model_property, "ar2")[[1]]
      model_property_df$filepath <- basename(fp)
      # print(model_property_df)
      model_property_df_list[[i]] <- model_property_df
      # increase counter
      i = i+1
    }
  }
}

model_property_df <- as.data.frame(do.call(rbind, model_property_df_list))
model_property_df

write.csv(model_property_df, file = file.path(getwd(),"Exported_Data","model_summaries_df",
                                              sprintf("%s_Adaptation_%s.csv", y_var,Sys.Date())))
```

<!-- # Import residential transaction price -->
<!-- ```{r} -->
<!-- flood_residential_transaction <- file.path(getwd(),"Exported_Data","flood_residential_transaction.csv") -->
<!-- flood_residential_transaction <- read.csv(flood_residential_transaction) -->
<!-- flood_residential_transaction -->
<!-- ``` -->
<!-- ```{r} -->
<!-- names(flood_residential_transaction) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- names(flood_residential_transaction) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- transaction_df <- flood_residential_transaction%>% -->
<!--   mutate_at(c("Date"), as.Date)%>% -->
<!--   mutate(month_year = format(Date,format="%Y-%m"))%>% -->
<!--   # log price -->
<!--   mutate(log_price_psm = log(Unit.Price....PSM.))%>% -->
<!--   # replace NA with a placeholder value e.g. 1000 -->
<!--   mutate(weeks_since_flood_clean = ifelse(is.na(weeks_since_flood), 1000, weeks_since_flood))%>% -->
<!--   # create bins of last flooded event -->
<!--   mutate( -->
<!--     flood_bin = cut( -->
<!--       weeks_since_flood_clean, -->
<!--       breaks = c(0, 4, 12, 52, 104,Inf), -->
<!--       labels = c("0_4w", "5_12w", "13_52w", "1yr_plus","MoreThan2yrs"), -->
<!--       right = TRUE -->
<!--     ) -->
<!--   )%>% -->
<!--   # convert chr to boolean -->
<!--   mutate_at(c("within_1km_school_car","within_2km_school_car", -->
<!--               "within_1km_school_walk","within_2km_school_walk","Is.parks.within.400m"),as.logical)%>% -->
<!--   mutate(Property_ownership = ifelse(Tenure=="Freehold",Tenure,"Leasehold"))%>% -->
<!--   mutate(Completion_date = as.numeric(ifelse(Completion.Date=="Uncompleted",substr(Tenure, nchar(Tenure)-3, nchar(Tenure)),Completion.Date)))%>% -->
<!--   mutate(Transaction_date = as.numeric(substr(Date,1,4)))%>% -->
<!--   mutate(Building_age = Transaction_date - Completion_date)%>% -->
<!--   mutate_at(c("Type.of.Sale","Type.of.Area","Property.Type","Postal.District","min_travel_time_work_region","PLN_AREA_N","Property_ownership","month_year","BUILDING"),as.factor)%>% -->
<!--   select(where(is.numeric)| where(is.factor) | where(is.logical))%>% -->
<!--   select(c("log_price_psm","Area..SQM.","Postal.District","busStops.within.200m","trainExits.within.400m","Floor.Level","min_distance_school_car","min_distance_school_walk","min_travel_time_work","betweeness_centrality","closeness_centrality","amenities..high_value_amenity..within.400m","amenities..negative_externality..within.400m","amenities..neutral..within.400m","malls.within.400m","Building_age","Type.of.Sale","Type.of.Area","Property.Type","PLN_AREA_N","min_travel_time_work_region","flood_bin","Property_ownership","within_1km_school_car","within_2km_school_car","within_1km_school_walk","within_2km_school_walk","Is.parks.within.400m","month_year","BUILDING")) -->

<!-- # rename columns -->
<!-- names(transaction_df) <- c("log_price_psm","Area_SQM","Postal_district","busStops_within_200m","trainExits_within_400m","Floor_level","min_distance_school_car","min_distance_school_walk","min_travel_time_work","betweeness_centrality","closeness_centrality","amenities_high_value_within_400m","amenities_negative_within_400m","amenities_neutral_within_400m","malls_within_400m","Building_age","Type_of_Sale","Type_of_Area","Property_Type","PLN_AREA_N","min_travel_time_work_region","flood_bin","Property_ownership","within_1km_school_car","within_2km_school_car","within_1km_school_walk","within_2km_school_walk","parks_within_400m","month_year","BUILDING") -->
<!-- transaction_df  -->
<!-- ``` -->



<!-- # Modelling approaches -->

<!-- ## using binned flood exposure -->

<!-- ```{r} -->
<!-- names(transaction_df) -->
<!-- ``` -->
<!-- ### Fixed-effects OLS estimation (feols) -->
<!-- ```{r} -->
<!-- flood_model_binned <-feols(log_price_psm~i(flood_bin, ref="0_4w")+Area_SQM+busStops_within_200m+trainExits_within_400m+Floor_level+min_distance_school_car+min_distance_school_walk+min_travel_time_work+betweeness_centrality+closeness_centrality+amenities_high_value_within_400m+amenities_negative_within_400m+amenities_neutral_within_400m+malls_within_400m+Building_age+Type_of_Sale+Type_of_Area+Property_Type+min_travel_time_work_region+Property_ownership+within_1km_school_car+within_2km_school_car+within_1km_school_walk+within_2km_school_walk+parks_within_400m | Postal_district+BUILDING+month_year, cluster = ~Postal_district, data=transaction_df) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- flood_model_binned -->
<!-- ``` -->
<!-- ```{r} -->
<!-- summary(flood_model_binned) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- model_summary <- summary(flood_model_binned) -->
<!-- class(model_summary) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- etable(flood_model_binned) -->
<!-- ``` -->


<!-- # ```{r} -->
<!-- # write.csv(etable(flood_model_binned), file.path(getwd(),"Exported_Data","fixed_effect_model.csv")) -->
<!-- # ``` -->
<!-- #  -->
<!-- # [Singapore Districts and their Origins](https://www.fraxtor.com/singapore-districts-and-their-origins/#:~:text=Although%20this%20system%20is%20no,%2C%2026%2C%2027%2C%2028.) -->
<!-- #  -->
<!-- # - See map of postal district -->
<!-- #  -->
<!-- # - This system was changed in 1979 to have four-digit postal codes, which included the district number followed by sector numbers. -->
<!-- #  -->
<!-- # - Singapore is also divided into three regions: the Core Central Region (CCR), Rest of Central Region (RCR), and Outside Central Region (OCR). The CCR is made up of districts 1, 2, 6, 9, 10, 11; the RCR consists of districts 3, 4, 5, 7, 8, 12, 13, 14, 15, 20; the OCR is made up of the other districts which are 16, 17, 18,19, 21, 22, 23, 24, 25, 26, 27, 28. -->
<!-- #  -->
<!-- # ```{r} -->
<!-- # length(unique(flood_residential_transaction$Postal.District)) -->
<!-- # ``` -->

