---
title: "econometric_analysis_20251126"
output: html_document
date: "2025-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(fixest)
# library(stargazer)
library(modelsummary)
```

# Initialise FE and cluster parameters

```{r}
fe_vars <- c("Building_Name","month_year")
cluster_vars <- c("SUBZONE_N")
y_var <- "log_price_PSM"
```


# Import residential transaction price

```{r}
# flood_residential_transaction <- file.path(getwd(),"Exported_Data","flood_residential_transaction_20251126.csv")
# flood_residential_transaction <- file.path(getwd(),"Exported_Data","flood_residential_transaction_20251128.csv")

# flood_residential_transaction_20260114.csv models the road raising network buffer
flood_residential_fp <- file.path(getwd(),"Exported_Data","flood_residential_transaction_20260114-3.csv")
flood_residential_transaction <- read.csv(flood_residential_fp)
flood_residential_transaction

```

# unique filename for saving results
```{r}
# unique filename
save_fp <- unlist(strsplit(basename(flood_residential_fp),"[_.]"))
save_fp <- save_fp[length(save_fp)-1]
save_fp <-paste(c(save_fp,paste(fe_vars,collapse="-"),y_var),collapse="_")
save_fp
```

```{r}
names(flood_residential_transaction)
```

Rule of Thumb If a variable represents categories → convert it to factor. If a variable is a free-text identifier, label, or description → keep it as character.

Because fixest automatically treats factors as categorical variables and generates the appropriate dummy variables internally.

Character variables are NOT treated as categorical — they must be converted to factor before being used as regressors or fixed effects.

✅ When do you use as.factor()?

Use as.factor() when You want the variable to appear as a categorical predictor (dummy variables).

# transaction_df
```{r}
transaction_df <- flood_residential_transaction%>%
  # y-dependent variable
  mutate(log_price_PSM = log(Unit_Price_.._PSM.))%>%
  # convert to factors so fixest will create dummy variables
  mutate_at(c("Type_of_Sale","Type_of_Area","Property_Type","Tenure",
              "Postal_District","Postal_Sector",
              "PLN_AREA_N","SUBZONE_N","REGION_N",
              "min_travel_time_work_region","stn_lines",
              "work_categories","drainage_period"),as.factor)%>%
  # convert to boolean
  mutate_at(c("within_6_months_post_flood","within_12_months_post_flood","within_18_months_post_flood",
              "parks_within_400m","is_ground_floor","prone_to_high_tide","within_flooding_hotspot"),as.logical)%>%
  # create month-year column as we want month_year to be the fixed effect
  mutate(month_year = as.factor(paste(month, year, sep = "_")))%>%
  # drop columns
  select(-c("Transacted_Price_...",                       # irrelevant to be control vars
            "Sale_Date",                                  # irrelevant to be control vars
            "Unit_Price_.._PSM.",                         # remove the other y-dependent var
            "year","month",                               # remove since year-month is the fixed effect
            "Project_Name",                              # remove the other potential spatial fixed effect
            "Address",                                    # remove the other potential spatial fixed effect
            # absorbed by strong project/building FEs 
            "Type_of_Area",# absorbed by strong project/building FEs. Require Property Type for filtering
            "Tenure",                                       # absorbed by strong project/building FEs
            "Completion_Date",                              # absorbed by strong project/building FEs 
            "Postal_Code","Postal_District","Postal_Sector",# absorbed by strong project/building FEs
            "REGION_N","PLN_AREA_N",                        # absorbed by strong project/building FEs, use subzone for clustering residuals
            "DOWNTOWN_CORE_travel_time","TAMPINES_travel_time",      # absorbed by strong project/building FEs
            "WOODLANDS_travel_time","ANG_MO_KIO_travel_time",        # absorbed by strong project/building FEs
            "JURONG_EAST_travel_time","min_travel_time_work_region", # absorbed by strong project/building FEs
            "min_travel_time_work","sch_within_1km_car",             # absorbed by strong project/building FEs
            "sch_within_2km_car","sch_min_distance_car",             # absorbed by strong project/building FEs
            "sch_within_1km_walk","sch_within_2km_walk",             # absorbed by strong project/building FEs
            # "betweeness_centrality","closeness_centrality",          # absorbed by strong project/building FEs      
            "sch_min_distance_walk","malls_within_400m",             # absorbed by strong project/building FEs
            "parks_within_400m","DEM",                               # absorbed by strong project/building FEs
            "drainage_density_.km_km2."                              # can be removed since it is absorbed by month-year FE
            )            
         )
  
  
transaction_df
```

## Visualise df


```{r}
datasummary_skim(transaction_df)
names(transaction_df)
```




# feols_formula
- To parse formulas, taking into account of control variables, fixed effects

## interaction_combinations


```{r}
interaction_combinations = function(...){
  # ... accepts an arbitrary number of arguments (both named and unnamed)
  # Returns: find all combinations input vectors
  
  combi <- expand.grid(...)
  
  as.vector(lapply(seq_len(nrow(combi)), function(i) as.character(unlist(combi[i, ]))))
}

# test output
interaction_combinations(c("within_6_months_post_flood","within_flooding_hotspot"),
                         c("prone_to_high_tide"),
            c("adaption1","adaptation2"))
```

## formula parser

TODO: add another argument in feols_formula such that we can directly specify the interactions instead of finding all combinations. If either one is supplied, it will override the others
```{r}
feols_formula = function(y_var, control_vars, fe_vars,cluster_vars,
                         interaction_vars=NA, 
                         specified_interaction_vars=NA,
                         interaction_sep="*"){
  # y_var (chr): y variable
  # control_vars (vector): control variables
  # interaction_vars (vector of vector): interaction variables
  # fe_vars (vector): fixed effect variables
  # specified_interaction_vars (vector of str): vector of specified interaction e.g. c(a*b, a:c, b:c)
  # interaction_sep (chr): separator e.g. "*" or ":"
  # "*" includes the main effects and the interaction
  # ":" includes the interactions ONLY
  control_vars_OG <- control_vars
  
  if (!any(is.na(interaction_vars))){
    # flatten interaction list
    interaction_list <- unlist(interaction_vars)
    # ensure that same variables do not appear in control vars, otherwise the main effects are included
    control_vars <- setdiff(control_vars_OG, interaction_list)
  }
  
  if (!any(is.na(specified_interaction_vars))){
    # if specified_interaction_vars is not NA, overwrite the previous interaction vars
    specified_interaction_list <- sapply(specified_interaction_vars, function(x) {
      strsplit(x,"[:* ]+") # split string by delimiter e.g. :, and *
    })
    specified_interaction_list <- unlist(specified_interaction_list)
    # ensure that same variables do not appear in control vars, otherwise the main effects are included
    control_vars <- setdiff(control_vars, specified_interaction_list)
    # print(control_vars)
  }
  
  control_vars <- setdiff(control_vars, fe_vars)
  control_vars <- setdiff(control_vars,c(y_var))
  control_vars <- setdiff(control_vars, cluster_vars)
  
  # collapse interaction vars
  if (!any(is.na(interaction_vars))){
    # combine interaction terms
    itn_terms <- sapply(interaction_vars, function(x) {
      paste(x,collapse=interaction_sep)
    })
    # collapse interaction terms using +
    itn_terms <- paste(itn_terms, collapse=" + ")
  } 
  
  # collapse specified interaction vars
  if (!any(is.na(specified_interaction_vars))){
    # collapse interaction terms using +
    specified_itn_terms <- paste(specified_interaction_vars, collapse=" + ")
    
    # combine with the prev interaction vars if its not NA
    if (!any(is.na(interaction_vars))) {
      itn_terms <- paste(c(itn_terms, specified_itn_terms), collapse=" + ")
    } else { # if prev interaction vars is NA, then override
      itn_terms <- specified_itn_terms
    }
    
  }
  
  # collapse control vars
  control_terms <-paste(control_vars, collapse = " + ")
  
  if (!any(is.na(interaction_vars)) | !any(is.na(specified_interaction_vars))){
    # combine control and interaction terms
    control_terms <- paste(control_terms, itn_terms, sep=" + ")
  }
  
  # collapse fe terms
  fe_terms <- paste(fe_vars, collapse = " + ")
  
  # combine all terms
  formula <- as.formula(paste(y_var,"~", control_terms, "|", fe_terms))
  
  cluster_vars <- as.formula(paste("~",paste(cluster_vars, collapse = " + ")))
  
  # return as a vector
  list("formula"=formula,"cluster"=cluster_vars)
}

# test output
feols_formula(y_var = "log_price",control_vars=names(transaction_df),
              interaction_vars =  interaction_combinations(
                  hazards = c("within_6_months_post_flood","within_flooding_hotspot"),
                  vulnerability = c("prone_to_high_tide"),
                  adaptation = c("adaptation1","adaptation2")
                  ),
              interaction_sep = "*",
              fe_vars = c("Project_Name","month_year"),
              cluster_vars = c("SUBZONE_N"),
              specified_interaction_vars = c("within_6_months_post_flood : closeness_centrality",
                                             "within_12_months_post_flood : betweeness_centrality")
              )

# feols_formula(y_var = "log_price",control_vars=names(transaction_df),
#               specified_interaction_vars = c("within_6_months_post_flood: closeness_centrality",
#                                               "within_12_months_post_flood: betweeness_centrality"),
#               interaction_sep = "*",
#               fe_vars = c("Project_Name","month_year"),
#               cluster_vars = c("SUBZONE_N")
#               )

```







### Fixed-effects OLS estimation (feols)

✅ 1. What is the cluster argument in feols()?

The cluster = argument tells fixest how to compute robust standard errors.

It does not change coefficient estimates.

It only changes:

- the estimated standard errors, t-stats, p-values, statistical significance

Clustering adjusts for within-group correlation (heteroskedasticity + autocorrelation + spatial correlation).

Common use-cases:

- transactions within the same district share the same economic shocks

- transactions in the same month have correlated errors

- properties near each other have correlated errors

- repeated transactions of same property


# Hedonic models

## Building attributes only

```{r}
names(transaction_df)
```

```{r}
model_property_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:13)],
                                                             c("betweeness_centrality","closeness_centrality")),
              interaction_vars = NA,
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_property_formula

# model where fixed effects are project name and month_year
model_property <- feols(
  model_property_formula$formula,
  cluster = model_property_formula$cluster,
  data = transaction_df
)
summary(model_property)
# display model outputs
etable(model_property)
```
## 0: Baseline model - flood hotspot

### 0A: Effect of flood on prices on private apartment located in flood-spot regions versus non-flood-spot regions

```{r}
names(transaction_df)
```


```{r}
model_0a_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality")),
              interaction_vars =  interaction_combinations(
                  hazards = c("within_6_months_post_flood","within_12_months_post_flood","within_18_months_post_flood",
                              "weeks_since_flood"),
                  vulnerability = c("within_flooding_hotspot")
                  ),
              interaction_sep = "*",
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_0a_formula

# model where fixed effects are project name and month_year
model_0a <- feols(
  model_0a_formula$formula,
  cluster = model_0a_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Condominium/Apartment")
)
summary(model_0a)
# display model outputs
etable(model_0a)
```
### 0B: Effect of flood on prices on landed property

- By default, all landed properties should have ground floor


```{r}
model_0b_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                              "betweeness_centrality","closeness_centrality",
                                                               "is_ground_floor","Floor_level")),
              interaction_vars =  interaction_combinations(
                  hazards = c("within_6_months_post_flood","within_12_months_post_flood","within_18_months_post_flood",
                              "weeks_since_flood"),
                  vulnerability = c("within_flooding_hotspot")
                  ),
              interaction_sep = "*",
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_0b_formula

# model where fixed effects are project name and month_year
model_0b <- feols(
  model_0b_formula$formula,
  cluster = model_0b_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Landed")
)
summary(model_0b)
# display model outputs
etable(model_0b)
```

## 1: Baseline model - flood occurrence

### 1A: Effect of flood on prices on private apartment's ground floor units

```{r}
names(transaction_df)
```

```{r}
model_1a_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type","prone_to_high_tide",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "within_flooding_hotspot")),
              interaction_vars =  interaction_combinations(
                  hazards = c("within_6_months_post_flood","within_12_months_post_flood","within_18_months_post_flood",
                              "weeks_since_flood"),
                  vulnerability = c("is_ground_floor")
                  ),
              interaction_sep = "*",
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_1a_formula

# model where fixed effects are project name and month_year
model_1a <- feols(
  model_1a_formula$formula,
  cluster = model_1a_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Condominium/Apartment")
)
summary(model_1a)
# display model outputs
etable(model_1a)
```

### 1B: Effect of flood on prices on landed property

- By default, all landed properties should have ground floor


```{r}
model_1b_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","is_ground_floor",
                                                               "Floor_level","Property_Type",
                                                               "within_flooding_hotspot",
                                                               "betweeness_centrality","closeness_centrality")),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_1b_formula

# model where fixed effects are project name and month_year
model_1b <- feols(
  model_1b_formula$formula,
  cluster = model_1b_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Landed")
)
summary(model_1b)
# display model outputs
etable(model_1b)
```

## 2: Heterogeneity by floor levels for tide-prone vs non-tide prone private apartment

- Effect if flood on prices within tide-prone vs non-tide-prone private apartment by floor levels
  - TODO: Conduct robustness check by varying to within_12/18_months_post_flood
- Within-building vertical sorting

### 2A: Continuous floor levels

```{r}
model_2a_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood",
                                                               "betweeness_centrality","closeness_centrality")),
              interaction_vars = interaction_combinations(
                                            hazard=c("within_6_months_post_flood"),
                                            vulnerability=c("Floor_level")),
              interaction_sep = "*",
              specified_interaction_vars = c("within_6_months_post_flood : prone_to_high_tide",
                                             "within_6_months_post_flood : prone_to_high_tide : Floor_level"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_2a_formula

# model where fixed effects are project name and month_year
model_2a <- feols(
  model_2a_formula$formula,
  cluster = model_2a_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Condominium/Apartment")
)
summary(model_2a)
# display model outputs
etable(model_2a)
```
### 2B: Floor ordinal categories (for better interpretability)

```{r}
model_2b_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood",
                                                               "betweeness_centrality","closeness_centrality")),
              interaction_vars = interaction_combinations(
                                            hazard=c("within_6_months_post_flood"),
                                            vulnerability=c("Floor_level")),
              interaction_sep = "*",
              specified_interaction_vars = c("within_6_months_post_flood : prone_to_high_tide",
                                             "within_6_months_post_flood : prone_to_high_tide : Floor_level"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_2b_formula

# model where fixed effects are project name and month_year
model_2b <- feols(
  model_2b_formula$formula,
  cluster = model_2b_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Condominium/Apartment")%>%
        mutate_at(c("Floor_level"), function(x) {
          as.factor(cut(x, breaks=c(-Inf, 3, 10, Inf), labels=c("low","middle","high")))}
          # as.factor(cut(x, breaks=c(-Inf, 5, 20, Inf), labels=c("low","middle","high")))}
                  )
)
summary(model_2b)
# display model outputs
etable(model_2b)
```


## 3: Heterogeneity by coastal properties (i.e. tide-prone vs non-tide prone) for ground floor units

- Effect of flood on prices across ground-floor units by tide-proneness. 
  - I.e. Among ground floor units only, does flood exposure affect prices differently in tide-prone vs non-tide prone projects/building
  - This allows us to isolate pure coastal backflow/drainage constraints
  - TODO: Conduct robustness check by varying to within_12/18_months_post_flood
- Horizontal vulnerability

```{r}
model_3_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood",
                                                               "is_ground_floor","Floor_level",
                                                               "betweeness_centrality","closeness_centrality")),
              
              specified_interaction_vars = c("within_6_months_post_flood",
                                             "within_6_months_post_flood : prone_to_high_tide"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_3_formula

# model where fixed effects are project name and month_year
model_3 <- feols(
  model_3_formula$formula,
  cluster = model_3_formula$cluster,
  data = transaction_df%>%
        filter(is_ground_floor == TRUE)
)
summary(model_3)
# display model outputs
etable(model_3)
```

## 4: Heterogeneity by centrality

- Effect of flood on prices by centrality
  - i.e. Do floods matter less or more in highly connected/accessible locations?

```{r}
model_4_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df)[c(1:18)],
                                                             c("stn_lines","Property_Type",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood"
                                                               )),
              
              specified_interaction_vars = c("within_6_months_post_flood",
                                             "within_6_months_post_flood : betweeness_centrality",
                                             "within_6_months_post_flood : closeness_centrality"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_4_formula

# model where fixed effects are project name and month_year
model_4 <- feols(
  model_4_formula$formula,
  cluster = model_4_formula$cluster,
  data = transaction_df
)
summary(model_4)
# display model outputs
etable(model_4)
```
## 5: Heterogeneity by flood adaptation measures

### 5.0A: How does adaptation moderate the effect of flood on prices on private apartment located in flood-spot regions versus non-flood-spot regions

- does that even make sense? because if it's in a flood prone area that means flood adaptation hasnt been implemented. The effect of flood adaptation may already be absorbed in the non-flood prone area already
- or it could be interpreted as exogenous impacts from flood adaptation works on flood prone area


```{r}
model_5a_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("within_flooding_hotspot",
                                             "work_categories : drainage_period",
                                             # vulnerability
                                            "within_flooding_hotspot : work_categories : drainage_period"
                                            # "is_ground_floor : work_categories : drainage_period"
                                            ),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5a_formula

# model where fixed effects are project name and month_year
model_5a <- feols(
  model_5a_formula$formula,
  cluster = model_5a_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Condominium/Apartment")
)
summary(model_5a)
# display model outputs
etable(model_5a)
```
### 5.0B: How does adaptation moderate the effect of flood on prices on landed properties located in flood-spot regions versus non-flood-spot regions

```{r}
model_5b_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("within_flooding_hotspot",
                                             "work_categories : drainage_period",
                                            "within_flooding_hotspot : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5b_formula

# model where fixed effects are project name and month_year
model_5b <- feols(
  model_5b_formula$formula,
  cluster = model_5b_formula$cluster,
  data = transaction_df%>%
        filter(Property_Type == "Landed")
)
summary(model_5b)
# display model outputs
etable(model_5b)
```
### 5.1A: How does adaptation moderate the effect of flood on prices on private apartment's ground floor units

```{r}
model_5c_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("is_ground_floor",
                                             "work_categories : drainage_period",
                                            "within_6_months_post_flood : is_ground_floor : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5c_formula

# model where fixed effects are project name and month_year
model_5c <- feols(
  model_5c_formula$formula,
  cluster = model_5c_formula$cluster,
  data = transaction_df%>%
    filter(Property_Type == "Condominium/Apartment")
)
summary(model_5c)
# display model outputs
etable(model_5c)
```
### 5.1B: How does adaptation moderate the effect of flood on prices for landed properties

```{r}
model_5d_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("work_categories : drainage_period",
                                            "within_6_months_post_flood : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5d_formula

# model where fixed effects are project name and month_year
model_5d <- feols(
  model_5d_formula$formula,
  cluster = model_5d_formula$cluster,
  data = transaction_df%>%
    filter(Property_Type == "Landed")
)
summary(model_5d)
# display model outputs
etable(model_5d)
```
### 5.2A: How does adaptation moderate the effect of flood on prices by floor levels for tide-prone vs non-tide prone private apartment

```{r}
model_5e_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              
              specified_interaction_vars = c("Floor_level",
                                            "Floor_level : prone_to_high_tide : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5e_formula

# model where fixed effects are project name and month_year
model_5e <- feols(
  model_5e_formula$formula,
  cluster = model_5e_formula$cluster,
  data = transaction_df%>%
    filter(Property_Type == "Condominium/Apartment")
)
summary(model_5e)
# display model outputs
etable(model_5e)
```


### 5.2B: How does adaptation moderate the effect of flood on prices by Floor categories for tide-prone vs non-tide prone private apartment

```{r}
model_5f_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              
              specified_interaction_vars = c("Floor_level",
                                             "work_categories : drainage_period",
                                            "Floor_level : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5f_formula

# model where fixed effects are project name and month_year
model_5f <- feols(
  model_5f_formula$formula,
  cluster = model_5f_formula$cluster,
  data = transaction_df%>%
    filter(Property_Type == "Condominium/Apartment")%>%
        mutate_at(c("Floor_level"), function(x) {
          as.factor(cut(x, breaks=c(-Inf, 3, 10, Inf), labels=c("low","middle","high")))}
          # as.factor(cut(x, breaks=c(-Inf, 5, 20, Inf), labels=c("low","middle","high")))}
                  )
)
summary(model_5f)
# display model outputs
etable(model_5f)
```

### 5.3: How does adaptation moderate the effect of flood on prices by coastal properties (i.e. tide-prone vs non-tide prone) for ground floor units

```{r}
model_5g_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("work_categories : drainage_period",
                                            "prone_to_high_tide : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5g_formula

# model where fixed effects are project name and month_year
model_5g <- feols(
  model_5g_formula$formula,
  cluster = model_5g_formula$cluster,
  data = transaction_df%>%
    filter(is_ground_floor == TRUE)
)
summary(model_5g)
# display model outputs
etable(model_5g)
```

### 5.4: How does adaptation moderate the effect of flood on prices by centrality

```{r}
model_5h_formula <- feols_formula(y_var = y_var,
                                        control_vars=setdiff(names(transaction_df),
                                                             c("stn_lines","Property_Type",
                                                               "betweeness_centrality","closeness_centrality",
                                                               "prone_to_high_tide",
                                                               "within_flooding_hotspot",
                                                               "is_ground_floor","Floor_level",
                                                               "within_6_months_post_flood",
                                                               "within_12_months_post_flood", 
                                                               "within_18_months_post_flood",
                                                               "weeks_since_flood")),

              specified_interaction_vars = c("work_categories : drainage_period",
                                            "betweeness_centrality : work_categories : drainage_period",
                                            "closeness_centrality : work_categories : drainage_period"),
              fe_vars = fe_vars,
              cluster_vars = cluster_vars
              )
model_5g_formula

# model where fixed effects are project name and month_year
model_5h <- feols(
  model_5h_formula$formula,
  cluster = model_5h_formula$cluster,
  data = transaction_df
)
summary(model_5h)
# display model outputs
etable(model_5h)
```

# Display model results side-by-side


```{r}
library(tinytable)

models_hazard_vul <- list(model_0a,model_0b,
                          model_1a,model_1b,
                          model_2a,model_2b,
                          model_3,model_4)
names(models_hazard_vul) <- paste0("(",c(1:length(models_hazard_vul)),")")

modelsummary(models_hazard_vul, stars = TRUE)
# export data
modelsummary(models_hazard_vul, stars = TRUE, gof_omit = "IC|F|Log|AIC|BIC", output = 
  file.path(getwd(),"Exported_Data","model_summaries",sprintf("models_hazard_vul_%s.docx",save_fp)))
```

```{r}
models_vul_adaptation <- list(model_5a,model_5b,
                               model_5c,model_5d,
                               model_5e,model_5f,
                               model_5g,model_5h)

names(models_vul_adaptation) <- paste0("(",c(1:length(models_vul_adaptation)),")")

modelsummary(models_vul_adaptation, stars = TRUE)
# export data
modelsummary(models_vul_adaptation, stars = TRUE, gof_omit = "IC|F|Log|AIC|BIC", output = file.path(getwd(),"Exported_Data","model_summaries",sprintf("models_vul_adaptation_%s.docx",save_fp)))
```


## plot coefficients

```{r}
# modelplot(model_fe_project_MY, coef_omit = "Intercept")
```

