---
title: "stacked_did"
output: html_document
date: "2026-04-03"
---

# import libraries
```{r}
library(dplyr)
library(tidyr)
library(fixest)
# library(stargazer)
library(modelsummary)
library(stringr)
library(ggplot2)
library(reshape2)
library(did)
# source("R_scripts/helper_functions.R")
source("R_scripts/feols_utils.R")
source("R_scripts/stacked_did.R")
```

# Import buffer dfs (Episodic flooding)

```{r}
import_files = function(fp_list){
  df_list <- lapply(fp_list, function(fp){
    
    factor_vars <- c("Type_of_Sale","SUBZONE_N","PLN_AREA_N","REGION_N","Property_Type")
    logical_vars <- c("is_ground_floor")
    read.csv(fp)%>%
      mutate(log_price_PSM = log(Unit_Price_.._PSM.),
            log_price = log(Transacted_Price_...),
            month_year = paste(month, year, sep = "_"))%>%
      mutate_at(all_of(factor_vars),as.factor)%>%
      mutate_at(all_of(logical_vars), function(x) as.integer(as.logical(x)))
  })
  # bind_rows(df_list, .id="id")
  df_list
}
small_radius <- seq(from=50, to=350, by =20)
big_radius <- round(sqrt(2)*small_radius,-1)

# dir
buffer_dir <- file.path(getwd(),"Exported_Data","stacked_did")
# fp names
fp_names <- mapply(function(x,y){
  sprintf("dsmall%03ddbig%03d",x,y)
},small_radius,big_radius)

fp_list <- file.path(buffer_dir,sprintf("PrivRes_20260403_%s_networkDepthNone.csv", fp_names))
names(fp_list) <- fp_names
fp_list
buffer_df_list <- import_files(fp_list)
buffer_df_list[[1]]
```




# 1 TWFE - Generalised DiD TWFE


$$
Y_{it} = \beta_0 Treat_i + \beta_1Post_{it} + \beta_2 Treat_i\times Post_{it} + \gamma X_{it} + \lambda_i + \delta_t + \epsilon_{it} 
$$

```{r}
# params
y_var <- "log_price_PSM"#"log_price"#"log_price_PSM"
property_type <- "Condominium/Apartment" # "Landed"
cluster_vars <- c("SUBZONE_N")
fe_vars <- c("SUBZONE_N","month_year")

local_DID_df_list <- lapply(seq_along(buffer_df_list), function(i){
  # control variables
  control_vars <- c("Type_of_Sale","Area_.SQM.","Building_Age","Floor_level","is_ground_floor")
  
  # small radius, big radius (treatment, control group)
  name_df <- names(buffer_df_list)[i]
  small_radius <- strsplit(name_df,split="dsmall|dbig")[[1]][2]
  big_radius <- strsplit(name_df,split="dsmall|dbig")[[1]][3]
  
  # filter property type so we focus analysis on different panels
  local_DID_df <- buffer_df_list[[i]]%>%
    filter(Property_Type == property_type)%>%
    # filter(contaminated_rows==0)
    filter(potential_contamination==0)
  
  treat_vars <- c("treat")
  post_vars <- c("post")
  # model formula
  model_property_formula <- feols_formula(y_var = y_var,
                                          control_vars=c(control_vars, treat_vars,post_vars),
                                          specified_interaction_vars=c(
                                            sprintf("%s * %s", treat_vars,post_vars)
                                            ),
                                          interaction_sep = "*",
                                          fe_vars = fe_vars,
                                          cluster_vars = cluster_vars)
  
  print(model_property_formula)
  
  # fit TWFE model
  model_property <- feols(
    model_property_formula$formula,
    cluster = model_property_formula$cluster,
    data = local_DID_df
  )
  
  summary(model_property)
  results_df <- get_model_results(model_property, model_name = sprintf("Treat%s_Control%s",small_radius, big_radius))
  
  results_df
})
  
local_DID_df_list <- as.data.frame(do.call(rbind, local_DID_df_list))
# export data
write.csv(local_DID_df_list,file.path(buffer_dir,"processed_outputs",
                        sprintf("episodicFlood_stackedDID_TWFE_%s.csv","potentialcontamination_removed")
                        ),
            row.names = FALSE)
local_DID_df_list
```

## 1.1 plot robustness
```{r}
model_names <- c("contaminated","contaminated_removed", "potentialcontamination_removed")

sapply(model_names, function(x){
  plot_local_DID_robustness(fp = file.path(buffer_dir,"processed_outputs",
                        sprintf("episodicFlood_stackedDID_TWFE_%s.csv",x)
                        ),

                        save_fp=file.path(getwd(),"Exported_Data","exported_figures",
                        sprintf("episodicFlood_stackedDID_TWFE_%s.svg",x)
                        ),
                        
                        filter_regex="^treat|^post",
                        significance_regex = "\\*+|\\."
                        )
})

```

# 2 Event study (flood causality)

$$
Y_{it} = \lambda_i + \delta_t + Treat_i + \sum_{k\geq-12, k\neq\{-1,0\}}^{k=12}(D_{it}^k \cdot \beta_k) + \epsilon_{it} 
$$

- where $D_{it}^k = 1$ if individual $i$ has been exposed to the treatment for $k$ periods in period $t$, and $D_{it}^k = 0$ otherwise.  To be clear here, it is helpful to give some examples.  Suppose individual $i$ becomes treated in period 3.  Then,

* $D_{it}^0 = 1$ when $t=3$ and is equal to 0 in other time periods

* $D_{it}^2 = 1$ when $t=5$ and is equal to 0 in other time periods

* $D_{it}^{-2} = 1$ when $t=1$ and is equal to 0 in other time periods.



## 2.1 Plot distribution of period_D
```{r}
period_D_list <- seq(-24,12,1)
# combine all dfs together
bind_rows(buffer_df_list, .id="id")%>%
  select(id,period_D)%>%
  filter(period_D  %in% period_D_list)%>%
  ggplot(aes(x=period_D)) +
    geom_density(fill="#69b3a2") +
    facet_wrap(vars(id)) +
    labs(x="Dt") +
    theme_bw()

ggsave(filename = file.path(getwd(),"Exported_Data","exported_figures",
                        sprintf("period_D_%s.svg","stackedDID")
                        ),
       width = 9, height = 5, units = "in")
```

## 2.2 Event study
```{r}
get_event_study_df = function(buffer_df, period_D_list, base_period=-1){
  # period_D_list (vector): list of period D list to obtain
  # base_period (int): base period of event study, usually just before the event e.g. -1
  
  base_period <- sprintf("Dt%s",sub("-","min", base_period))
  
  # filter relevant periods
  buffer_df <- buffer_df%>%
    # filter((period_D >= min_period_D) & (period_D <= max_period_D))%>%
    filter(period_D  %in% period_D_list)%>%
    # create index to merge back dummy variables later
    mutate(index = row_number())
  
  # create dummy variables from period_D
  Dt_df <- buffer_df%>%
    dcast(index~period_D, fun.aggregate=length)
  
  names(Dt_df) <- c("index",sprintf("Dt%s",sub("-","min",
                                               names(Dt_df)[c(2:length(names(Dt_df)))]
                                               )
                                    ))
  buffer_df <- merge(buffer_df, Dt_df,by=c("index"))
  # drop base period column but keep observations associated to it
  buffer_df <- buffer_df%>%
    select(-all_of(base_period))
  
  # identify Dt vars
  Dt_vars <- names(buffer_df)[grepl("^Dt.*",names(buffer_df))]
  Dt_vars
}

get_event_study_df(buffer_df_list[[1]], period_D_list = seq(-12,6,1), base_period=-1)
# # create Dt dummy variables using flood period
#   Dt_df <- buffer_df%>%
#     mutate(period_D = period_sale - !!as.name(period_flood_var))%>%
#     mutate_at(vars(period_D), function(x) ifelse(x <= -12,  -12, ifelse(x >= 12, 12, x)))%>%
#     dcast(index~period_D, fun.aggregate=length)
```

